---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# consensusNetR


<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

consensusNetR is an R Package for combining networks into a consensus network based on the work of [Laura Cantini and Andrei Zinovyev](https://academic.oup.com/bioinformatics/article/35/21/4307/5426054). In addition to identifying consensus based on correlation of community meta-genes (loadings or membership scores), we also implement methods based on overlap. 

## Installation

Install the version from BMS BioGit with:

```{r, eval=FALSE}
remotes::install_github(
  repo = "Systems-Immunology/consensusNetR", 
  host = "https://biogit.pri.bms.com/api/v3"
)
```

or:

```{r, eval=FALSE}
remotes::install_git(
  "https://biogit.pri.bms.com/Systems-Immunology/consensusNetR.git"
  )
```


## Code of Conduct
  
Please note that the icWGCNA project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


